---
title: "Project - Group 7 Zomato Restaurant Recommendation"
output:
  pdf_document:
    latex_engine: xelatex
---

Group Members:
1. Aman Maheshwari
2. Saloni Bhutada

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Problem Statement - To perform EDA on Zomato Restaurant Data and give recommendations of restaurants based on them. 

Step 1: Load libraries and datasets

Loading the all the necessary libraries

```{r}
library(stringr)
library(dplyr)
library(readxl)
library(tidyr)
library(dplyr)  
library(magrittr)
library(stringr)
library(lubridate)
library(lemon)
library(knitr)
library(ggplot2)
library(gridExtra)
library(libr)
library(lessR)
library(sf)
library(data.table)
library(maps)      
library(mapdata)    
```

We are loading the zomato and country code dataset in this step. 

```{r}
restaurant_data <- read.csv("/Users/salonihutada/Downloads/Zomato Data/zomato.csv")
#restaurant_data

country_code <- read_excel("/Users/salonihutada/Downloads/Zomato Data/Country-Code.xlsx")
#country_code
```

Step 2: Data Cleaning And Data Wrangling

We obtain the columns of our Zomato Restaurant's Main Dataset.

```{r}
#Used colnames() function to get the column names of the data
obtaining_columns_restaurant <- colnames(restaurant_data)
#obtaining_columns_restaurant

```

In the below code chunk using dim and summary we get the shape and summary of each column

```{r}
#To get the shape of the data we used dim()
dim(restaurant_data)


#To know the summary of the data used summary() 
summary(restaurant_data)


#Used the str() check for datatypes and some sample data of each columns 
str(restaurant_data)
```

We check for the null values and perform Null Treatment

```{r}
#Check for nulls in the price column using filter() - Average.Cost.for.two == 0
cities_with_avg_cost_zero <- restaurant_data %>% filter(Average.Cost.for.two == 0)
#cities_with_avg_cost_zero


#Since there are only few records with Average.Cost.for.two = 0, so we are dropping those records
dropping_zerocost_restaurant<-restaurant_data[restaurant_data$Average.Cost.for.two != 0, ]
#dropping_zerocost_restaurant


#Finally count the nulls in all columns using sum(is.na())
null_count <-  sapply(dropping_zerocost_restaurant, function(x) sum(is.na(x)))
null_count

```

To join both the table on Country_Code as key column

``` {r}
#Left join both the datasets using left_join() function
colnames(dropping_zerocost_restaurant)[3] <- "Country_Code"
colnames(country_code)[1] <- "Country_Code"
complete_restaurant_data <- left_join(dropping_zerocost_restaurant,country_code, by="Country_Code")
#complete_restaurant_data


#To remove , and split each values individually of rows we used strspilt() function
split <- strsplit(complete_restaurant_data$Cuisines, ",")
#unique(split)


#Calculated the count of each individual value and stored in a new column 
Cuisine_count<- complete_restaurant_data$Cuisines_count<- (sapply( split , length))
#Cuisine_count
```

To calculate the total records of each unique entry of the data

```{r}
#To get total records, group_by city, then using summarize() calculate total records of the cities 
Count_of_citywise_record <- complete_restaurant_data %>%
          group_by(City) %>%
          summarise(total_records=n())
Count_of_citywise_record


#To calculate total records, group_by city, then using summarize() calculate total records of the countries
Count_of_countrywise_record <- complete_restaurant_data %>%
  group_by(Country) %>%
  summarise(total_records=n())
Count_of_countrywise_record

```

Converted all the respective currencies of various countries to Dollar($) for better understanding.

```{r}

#To convert all the currency to dollar for further better understanding of average cost of two we used if-else condition and stored the updated price in new column
complete_restaurant_data <- datastep(complete_restaurant_data, {
  
  if (Currency == "Dollar($)")
    Average_cost_for_two <- Average.Cost.for.two * 1
  else if (Currency == "Botswana Pula(P)")
    Average_cost_for_two <- Average.Cost.for.two * 0.090
  else if (Currency == "Brazilian Real(R$)")
    Average_cost_for_two <- Average.Cost.for.two * 0.18
  else if (Currency == "Indian Rupees(Rs.)")
    Average_cost_for_two <- Average.Cost.for.two * 0.013
  else if (Currency == "Emirati Diram(AED)")
    Average_cost_for_two <- Average.Cost.for.two * 0.27
  else if (Currency == "Indonesian Rupiah(IDR)")
    Average_cost_for_two <- Average.Cost.for.two * 0.000071
  else if (Currency == "NewZealand($)")
    Average_cost_for_two <- Average.Cost.for.two * 0.72
  else if (Currency == "Pounds(£)")
    Average_cost_for_two <- Average.Cost.for.two * 1.38
  else if (Currency == "Qatari Rial(QR)")
    Average_cost_for_two <- Average.Cost.for.two * 0.27
  else if (Currency == "Rand(R)")
    Average_cost_for_two <- Average.Cost.for.two * 0.069
  else if (Currency == "Sri Lankan Rupee(LKR)")
    Average_cost_for_two <- Average.Cost.for.two * 0.0049
  else if (Currency == "Turkish Lira(TL)")
    Average_cost_for_two <- Average.Cost.for.two * 0.108
  
})
#complete_restaurant_data

```

1. Plotting a world map visualization to locate the locations of some best resturants of various countries

```{r}
#Map() and map.scale function was used to get the coordinates and the scale of the map
map('worldHires')
map.scale(160,0,relwidth = 0.15, metric = TRUE, ratio = TRUE)
map.scale(160,-40,relwidth = 0.15, metric = TRUE, ratio = TRUE)

#Created a new dataframe called as Excellent_Rating_restaurant_location which filters out the excellent rating restaurants and displays them with the other required columns
Excellent_Rating_restaurant_location <-complete_restaurant_data %>% 
  filter(Rating.text=='Excellent')  %>% 
  select(Restaurant.Name, Longitude, Latitude, Rating.text,Country)
#Excellent_Rating_restaurant_location


#Acquired map plot using map function as well as points() to plot latitude and longitude of all the best restaurants cities 
map('worldHires')
points(Excellent_Rating_restaurant_location$Longitude, Excellent_Rating_restaurant_location$Latitude,col=2,pch=20)

```

2A. Countries to visit for some of the best restaurants in the world - Barchart visual based on customer's ratings

```{r}
# Created a new dataframe called as Best_Restarants which has filter based on Aggregate ratings of the customers, grouped by Country and calculated their total records
Best_Resturants<- complete_restaurant_data %>% 
  filter(Aggregate.rating >= 4.0) %>% 
  select(Country,Aggregate.rating) %>% 
  group_by(Country) %>% 
  summarize(count =n())
#Best_Resturants


# Plotted a barchart visual using ggplot() function to display all the countries with amount of best restautants based on customer's feedback and the data
Best_Restuarant_Visual <- ggplot(Best_Resturants, aes(x=Country, y = count)) + 
  geom_bar(stat = "identity", fill="steelblue") +
  geom_text(aes(label=count), vjust=-0.3, size=3.5) +
  theme_minimal() +
  labs(title="Count of Best Restuarants to visit in various countries", 
       subtitle="Countrywise distributions")
Best_Restuarant_Visual

```

2B. Pie Chart Distribution to know Restaurant's category based on customer's rating 

```{r}
#Generated a new dataframe named as Restaurant_preference_piechart which segregates the customer's rating into 3 category Most Preferred, Average Preference and Least Preferred 
Restaurant_preference_piechart= complete_restaurant_data<- complete_restaurant_data %>% 
                               mutate(Restaurant_ratings =      case_when(complete_restaurant_data$Aggregate.rating >= 3.5 ~ "Most Preferred",
between(complete_restaurant_data$Aggregate.rating, 1.5,3.5) ~ "Average Preference", 
complete_restaurant_data$Aggregate.rating <= 1.5 ~ "Least Preferred" 
  ))
#Restaurant_preference_piechart

#To count the total values of Restaurant_preference categories we used dplyr()
Restaurant_preference_count <- Restaurant_preference_piechart %>%                            
                               group_by(Restaurant_ratings) %>%
                               summarise(count = n())
Restaurant_preference_count

#Plotted a piechart using pie() function which displays the overall percentage of each distribution
colors = c("orange", "indianred1", "paleturquoise") 
pie(table(complete_restaurant_data$Restaurant_ratings), main="Preference of Restuarants based on Ratings",col=colors)

```

3. Visualized top Fast Food restaurants in USA and India

```{r, echo=FALSE}
#Created Best_Fastfood dataframe with all the required filters and displayed the top Fast food restaurants of two countries
Cuisines_types <- c("Fast Food", "Pizza", "Burger")
Best_Fastfood<- complete_restaurant_data %>% 
  filter(Country %in% c("United States", "India") & Cuisines %in% Cuisines_types & Aggregate.rating >= 4.0) %>% 
  select(Restaurant.Name,Country, Aggregate.rating) %>% 
  group_by(Country) %>% 
  slice_max(Aggregate.rating, n = 5, with_ties = F) %>%
  arrange(desc(Country))
#Best_Fastfood


# Visualized top 5 Fast Food Restaurants in USA, India using ggplot() 
Best_Fastfood_Visual <-ggplot(Best_Fastfood, aes(fill=Restaurant.Name, y=Aggregate.rating, x=Country)) + 
  geom_col(width = 0.5, position = position_dodge(0.5)) +
  coord_cartesian(ylim=c(3.5, 5.0))
  theme_minimal() +
  labs(title="Top 5 Fast Food Restaurants to visit in various countries", 
       subtitle="Countrywise distributions")
Best_Fastfood_Visual

```

4. Visualized top specific cuisines Restaurants to try in USA, India

```{r}
#Created Best_Specific_Cusines_Restaurant dataframe with all the required filters and displayed best Specific Cuisines Restaurants to try in USA, India
Specific_Cuisines <- c("Chinese", "Italian", "American", "Indian", "Thai", "Japenese", "Mexican", "Asian")
Best_Specific_Cusines_Restaurant<- complete_restaurant_data %>% 
  filter(Country %in% c("United States","India") & split %in% Specific_Cuisines  & Aggregate.rating >= 3.5) %>% 
  select(Restaurant.Name,Country,Cuisines, Aggregate.rating, Average_cost_for_two) %>% 
  group_by(Country) %>% 
  slice_max(Aggregate.rating, n = 8, with_ties = F) %>%
  arrange(desc(Country))
#Best_Specific_Cusines_Restaurant


# Visualized Best Specific Cuisines Restaurants in USA, India using ggplot() 
Specific_Cuisines_Visual <-ggplot(Best_Specific_Cusines_Restaurant, aes(fill=Country, y=Aggregate.rating, x=Cuisines))+
  geom_col(width = 0.5, position = position_dodge(0.5)) +
  #geom_bar(stat = "identity") +
  coord_cartesian(ylim=c(3.5, 5.0))
  theme_minimal() +
  labs(title="Top specific cuisines Restaurants to visit in various countries", 
       subtitle="Countrywise distributions")
Specific_Cuisines_Visual

```

5. Visualized Fine Dining Restaurants to try in USA, India

```{r}
# Created Fine_Dining_for_Date dataframe with all the required filters and displayed Best Fine Dining Restaurants to try in USA, India
Specific_Cuisines <- c("Chinese", "Italian", "American", "Thai", "Japenese", "Mexican", "Asian")
Fine_Dining_for_Date<- complete_restaurant_data %>% 
  filter(Country %in% c("Phillipines","India", "UAE", "United Kingdom" ) & split %in% Specific_Cuisines  &      Aggregate.rating >= 3.5 & Has.Table.booking == "Yes") %>% 
  select(Restaurant.Name, Country, Cuisines, Aggregate.rating) %>% 
  group_by(Country) %>% 
  slice_max(Aggregate.rating, n = 40, with_ties = F) %>%
  arrange(desc(Country))
#Fine_Dining_for_Date


# Visualized Best Fine Dining Restaurants to try in USA, India using ggplot() 
Fine_Dining_for_Date <-ggplot(Fine_Dining_for_Date, aes(fill=Country, y=Aggregate.rating, x=Cuisines)) + 
  geom_col(width = 0.5, position = position_dodge(0.5)) +
  #geom_bar(stat = "identity") +
  coord_cartesian(ylim=c(3.5, 5.0))
  theme_minimal() +
  labs(title="Best Fine Dining Restaurants in USA, India to visit", 
       subtitle="Countrywise distributions")
Fine_Dining_for_Date

```

6. Visualized Best Cafes to hangout in UAE, India

```{r}
# Created Best_Cafe_for_Date dataframe with all the required filters and displayed top cafes in USA, India for Students -- Average_cost_for_two, Horizontal barchart
  Cafe_Seletion_for_Date <- c("Cafe","Beverages", "Coffee")
  Best_Cafe_for_Date<- complete_restaurant_data %>% 
    filter(Country %in% c("United States","India", "UAE") & split %in% Cafe_Seletion_for_Date & Aggregate.rating >=4.0) %>% 
    select(Restaurant.Name,Country,Cuisines, Aggregate.rating, Average_cost_for_two ) %>% 
    group_by(Country) %>% 
    slice_max(Aggregate.rating, n = 5, with_ties = F) %>%
    arrange(desc(Country))
  #Best_Cafe_for_Date
  
# Visualized Best Cafes to hangout in USA, India using ggplot()
Best_Cafe_for_Date_Visual <-ggplot(Best_Cafe_for_Date, aes(fill=Restaurant.Name, y=Aggregate.rating, x=Country)) + 
    geom_col(width = 0.5, position = position_dodge(0.5)) +
    #geom_bar(stat = "identity") +
    coord_cartesian(ylim=c(3.5, 5.0))
    theme_minimal() +
    labs(title=" Best Cafes to hangout in UAE, India", 
         subtitle="Countrywise distributions")
Best_Cafe_for_Date_Visual
```

7. Visualized maximum online deliveries available across top countries like USA, India & UAE.

```{r}
#Created Onlinedelivery_avaliable dataframe for cities with maximum online deliveries carried out
Onlinedelivery_avaliable<- complete_restaurant_data %>%
  filter(complete_restaurant_data$Has.Online.delivery =="Yes", Country %in% c("United States","India","UAE")) %>%
  group_by(City)  %>%
  summarise(Number_of_Online_Deliveries = n())%>%
  arrange(desc(Number_of_Online_Deliveries)) %>%
  head(10)
#Onlinedelivery_avaliable

#Visualized cities with maximum online deliveries carried out using ggplot()
Onlinedelivery_avaliable_visual<- ggplot(Onlinedelivery_avaliable, aes(x=City,fill = City , y=Number_of_Online_Deliveries)) +
  geom_bar(stat='identity')+
  ggtitle("Cities with Maximum Online Deliveries")+
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5))
  labs(x="Cities", y="Number of Online Deliveries")+
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_hline(yintercept=max(Onlinedelivery_avaliable$Number_of_Online_Deliveries), linetype="dashed")
Onlinedelivery_avaliable_visual
```

Conclusion: Using the Zomato Restaurant Dataset, which provides numerous characteristics for judging a restaurant such as ratings, votes, location, cuisines, and so on, we were able to effectively transform all of the business questions into the findings using EDA.


#Learning 
By this Project we got the basic understanding of how much importance a data analytics can play into multiple decision making process like, Where to open a new restaurant?, What is speciality of this restauarnt?, How much a meal can cost me?, etc.
This project covers the entire process, including data wrangling, cleaning, and EDA.
Along with the fundamental approach, we learned how to use libraries such as ggplot, maps, mapdata, sf, gridextra, and others.
We may deduce from this project that there are "n" viable business solutions that can be obtained by employing data analytics.


